\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-05-12 doc/sw-system.tex
Reverted title after more chat with Christine

\title[\SW]
{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses with Citizen Science}

@@

\item Each volunteer is assigned a simple software agent, characterised by a
confusion matrix~$\CM$. The two independent elements of this matrix are the
probabilities, as estimated by the agent, that the volunteer is going to be 1)
correct when they report that an image contains a lens when it really does
contain a lens, $\PL = \pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
an image does not contain a lens when it really doesn't contain a lens,
$\PD = \pr(\saidNOT|\NOT,T)$.

@@

For comparison we show the results of an analysis where the classifications of
training images were ignored, and the agents' confusion matrix elements
were instead all simply assigned initial values of 0.75
which then remained constant. This set-up emulates a
very simple unweighted voting scheme, where all classifications are treated
equally.  In this case, the TPR never reaches 80\% in \StageOne or 60\% in
\StageTwo, thus illustrating the benefit of including training images and
allowing the agents to learn via their Bayesian updates.
When the software agents are allowed to update their confusion matrices, the choice of
initial confusion matrix is not very important: the same 0.75 initial values
applied to normal, learning agents resulted in only a slightly lower TPR than
the default case.

>>>>

\title[\SW]
{\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses}

@@

\item Each volunteer is assigned a simple software agent, characterised by a
confusion matrix~$\CM$. The two independent elements of this matrix are the
probabilities, as estimated by the agent, that the volunteer is going to be 1)
correct when they report that an image contains a lens when it really does
contain a lens, $\PL = \pr(\saidLENS|\LENS,T)$, and 2) correct when they report that
an image does not contain a lens when it really doesn't contain a lens,
$\PD = \pr(\saidNOT|\NOT,T)$. The confusion matrix contains all the information
the agent has about how good its volunteer is at classifying images.

@@

For comparison we show the results of an analysis where the classifications of
training images were ignored, and the agents' confusion matrix elements
were instead all simply assigned initial values of 0.75,
which then remained constant. This set-up emulates a
very simple unweighted voting scheme, where all classifications are treated
equally.  In this case, the TPR never reaches 80\% in \StageOne or 60\% in
\StageTwo, thus illustrating the benefit of including training images and
allowing the agents to learn via their Bayesian updates.
When the software agents are allowed to update their confusion matrices,
the choice of
initial confusion matrix is not very important: the same 0.75 initial values
applied to normal, learning agents resulted in only a slightly lower TPR than
the default case.
